---
title: "p8105_hw6_ra2965"
output: github_document
---

```{r warning=FALSE, message=FALSE}
library(modelr)
library(tidyverse)

```

#Problem1

###Load the crude data and do data cleaning:

convert some variables to factor vectors:
```{r warning=FALSE, message=FALSE}
bwt = read_csv('./data/birthweight.csv')

bwt = bwt %>% 
  mutate(
    babysex = fct_infreq(as.factor(babysex)),
    frace = fct_infreq(as.factor(frace)),
    malform = fct_infreq(as.factor(malform)),
    mrace = fct_infreq(as.factor(mrace))
  )

#checking for missing data?
#bwt %>% 
#filter(is.na(wtgain))

```
There is no missing values.

###Propose a regression model for birthweight

The babies with larger head circumference may have higher birthweight. I hypothesized that the baby birthweight can be associated with bhead: baby’s head circumference at birth (centimeters):
```{r}
fit = lm(bwt ~ bhead, data = bwt)
```

```{r warning=FALSE, message=FALSE}
fit %>% 
  broom::tidy() %>% 
  as.tibble()
```
I tried to make a linear regression model with a predictor of momage, which is baby’s head circumference at birth (cm), and a outcome of baby birthweight(gram). The p value of the beta of momage is <0.05, which means that the baby birthweight(gram) is significantly associated with baby’s head circumference at birth (cm) at 5% level of significance.


```{r}
fit %>% 
  broom::glance() %>% 
  as.tibble()

```


```{r}
bwt %>% 
  modelr::add_residuals(fit) %>% 
  modelr::add_predictions(fit) %>% 
  select(momage, bwt, pred, resid) %>% 
  ggplot(aes(x = pred, y = resid)) + 
  geom_point() +
  labs(
    title = 'Model residuals against fitted values',
    x = 'Fitted values',
    y = 'Residuals'
  )
```

###Compare my model to two others:

One using length at birth and gestational age as predictors (main effects only):
```{r}
fit2 = lm(bwt ~ gaweeks + blength, data = bwt)
```

```{r}
fit3 = lm(bwt ~ bhead * blength + bhead * babysex + blength * babysex, data = bwt)
```




