---
title: "p8105_hw6_ra2965"
output: github_document
---

```{r warning=FALSE, message=FALSE}
library(modelr)
library(tidyverse)
library(mgcv)
```

#Problem1

###Load the crude data and do data cleaning:

convert some variables to factor vectors:
```{r warning=FALSE, message=FALSE}
bwt = read_csv('./data/birthweight.csv')

bwt = bwt %>% 
  mutate(
    babysex = fct_infreq(as.factor(babysex)),
    frace = fct_infreq(as.factor(frace)),
    malform = fct_infreq(as.factor(malform)),
    mrace = fct_infreq(as.factor(mrace))
  )

#checking for missing data?
#bwt %>% 
#filter(is.na(wtgain))

```
There is no missing values.

###Propose a regression model for birthweight

The babies with larger head circumference may have higher birthweight. I hypothesized that the baby birthweight can be associated with bhead: baby’s head circumference at birth (centimeters):
```{r}
bwt %>% 
  ggplot(aes(x = wtgain, y = bwt)) +
  geom_point()

```
It seems there is a positive association between x and y.

Fit a linear regression model:
```{r warning=FALSE, message=FALSE}

fit = lm(bwt ~ wtgain, data = bwt)

bwt %>% 
  add_predictions(fit) %>% 
  ggplot(aes(x = wtgain, y = bwt)) + 
  geom_point() +
  geom_line(aes(y = pred), color = "red")

fit %>% 
  broom::tidy() %>% 
  as.tibble()
fit %>% 
  broom::glance() %>% 
  as.tibble()

```
I tried to make a linear regression model with a predictor of mother’s weight gain during pregnancy (pounds), and a outcome of baby birthweight(gram). The p value of the beta of momage is <0.05, which means that the baby birthweight(gram) is significantly associated with mother’s weight gain during pregnancy at 5% level of significance.

###Show a plot of model residuals against fitted values:
```{r}
bwt %>% 
  add_predictions(fit) %>% 
  add_residuals(fit) %>% 
  select(wtgain, bwt, pred, resid) %>% 
  ggplot(aes(x = pred, y = resid)) + 
  geom_point() +
  labs(
    title = 'Model residuals against fitted values',
    x = 'Fitted values',
    y = 'Residuals'
  )
```

###Compare my model to two others:

One using length at birth and gestational age as predictors (main effects only):
```{r}
bwt_df = crossv_mc(bwt, 100) 
bwt_df =
  bwt_df %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble))

bwt_df = 
  bwt_df %>% 
  mutate(fit1_mod  = map(train, ~lm(bwt ~ wtgain, data = .x)),
         fit2_mod  = map(train, ~lm(bwt ~ gaweeks + blength, data = .x)),
         fit3_mod  = map(train, ~gam(bwt ~ bhead * blength + bhead * babysex + blength * babysex, data = .x))) %>% 
  mutate(rmse_fit1 = map2_dbl(fit1_mod, test, ~rmse(model = .x, data = .y)),
         rmse_fit2 = map2_dbl(fit2_mod, test, ~rmse(model = .x, data = .y)),
         rmse_fit3 = map2_dbl(fit3_mod, test, ~rmse(model = .x, data = .y)))

```

Make a plot showing the distribution of RMSE values for each candidate model:
```{r}
bwt_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```

According to the violine plot, the model using head circumference, length, sex, and all interactions (including the three-way interaction) between these factors as predictors is the best.



